The packaging requirements for the laser harp project identify how the delivered product will be packaged for delivery to the end-user and how it will "look" when finished and delivered. For example, the software required for operation will be pre-loaded on the included microSD card. The product will be delivered in a single package, ensuring all components are included and protected during shipping. Some components may require user assembly, with detailed instructions provided. The device will feature company branding and a professional finish. Care is taken not to duplicate requirements found in other sections of this document.


\subsection{Pre-loaded Software}
\subsubsection{Description}
The software required for the operation of the laser harp must be pre-loaded onto the included microSD card. This includes the operating system, necessary drivers, and the laser harp control software.
\subsubsection{Source}
Development Team, Customer
\subsubsection{Constraints}
Economic: Pre-loading software reduces the need for end-user installation support, lowering post-sale support costs.
Technical: The software must be thoroughly tested to ensure it works out-of-the-box.
Usability: Ensures a seamless user experience by reducing setup complexity.
\subsubsection{Standards}
ISO/IEC 25010: Systems and software Quality Requirements and Evaluation (SQuaRE) - System and software quality models.
\subsubsection{Priority}
High


\subsection{Single Package Delivery}
\subsubsection{Description}
All hardware components of the laser harp must be delivered in a single package. This package should include the main unit, power supply, USB receiver, user manual, and any necessary cables.
\subsubsection{Source}
Customer, Sponsor
\subsubsection{Constraints}
Economic: Consolidating packaging reduces shipping costs and potential damage during transport.
Environmental: Packaging materials should be recyclable to minimize environmental impact.
Health & Safety: Packaging must protect the components from damage during shipping and handling.
\subsubsection{Standards}
ISO 11607-1: Packaging for terminally sterilized medical devices - Requirements for materials, sterile barrier systems, and packaging systems.
\subsubsection{Priority}
High


\subsection{Customer Support Information}
\subsubsection{Description}
The package must include customer support information, such as a toll-free support number, email address, and website URL for troubleshooting and assistance.
\subsubsection{Source}
Customer, Sponsor
\subsubsection{Constraints}
Economic: Including support information helps reduce the need for returns and enhances customer satisfaction.
Usability: Information must be easy to find and clearly printed in the user manual.
\subsubsection{Standards}
ISO 10002 Quality management - Customer satisfaction - Guidelines for complaints handling in organizations.
\subsubsection{Priority}
Moderate/Future


\subsection{User-assembled Components}
\subsubsection{Description}
Some components of the laser harp, such as the frame and the laser modules, will be user-assembled. Detailed assembly instructions must be provided to guide users through this process.
\subsubsection{Source}
Development Team
\subsubsection{Constraints}
Economic: User assembly reduces manufacturing and shipping costs.
Usability: Instructions must be clear and easy to follow, with diagrams and step-by-step guidance.
Health & Safety: Assembly instructions must include safety warnings and precautions.
\subsubsection{Standards}
ISO 7000 Graphical symbols for use on equipment - Registered symbols.
\subsubsection{Priority}
Moderate


\subsection{Branding and Appearance}
\subsubsection{Description}
The laser harp must feature the company logo and branding. The main unit should be painted in the company’s colors and have a professional finish.
\subsubsection{Source}
Sponsor
\subsubsection{Constraints}
Economic: Branding should not significantly increase manufacturing costs.
Usability: The branding should not obscure any functional parts of the device.
Aesthetics: The device should have a professional and attractive appearance to enhance customer satisfaction.
\subsubsection{Standards}
ISO 3864-1: Graphical symbols - Safety colors and safety signs.
\subsubsection{Priority}
Low
